Enhanced proximity effect in zigzag-shaped Majorana Josephson junctions.

### 2019-03-12 paper/snakemajoranas.tex
mention more causes of a soft gap

\comment{The gap is small because of long trajectories.}
An important challenge in creating stable Majoranas is the appearance of a soft gap---a power law, instead of exponential decay of the density of states near zero energy.
It was shown previously that interface disorder and pairbreaking lead to a soft induced gap~\cite{takei_soft_2013}.
Even in systems with perfect interfaces and the absence of pairbreaking, states which have their momentum directed along the junction give rise to a soft gap~\cite{de_gennes_1963, beenakker_billiards_2005}.
From a semiclassical perspective, these momenta correspond to long paths through the semiconductor without interruption by the superconductor, shown in Fig.~\ref{fig:setup}(a).
These long trajectories have long flight times $\tau_\textrm{f} \approx L_\textrm{t} / v_F$ (see Fig.~\ref{fig:setup}), where $L_\textrm{t}$ is the trajectory length.
Equivalently, the Thouless energy of these trajectories $E_{\textrm{Th}}=\hbar / \tau_\textrm{f}$ is small, resulting in a small gap $E_\textrm{gap} \ll \Delta$.
This problem does not appear when the Fermi surface is small and the zero point motion dominates the transverse velocity, making a low filling of the bands a possible workaround\cite{Nijholt2015}.
However, low filling requires precise knowledge of the system and is more sensitive to disorder or microscopic inhomogeneities.
On the other hand, disorder scatters these long trajectories and introduces a cutoff on the scale of the mean free path~\cite{Haim2018}; however, disorder is impossible to control to a required precision experimentally.

>>>>

\comment{The gap is small because of long trajectories.}
An important challenge in creating stable Majoranas is the appearance of a soft gap---a power law decay instead of an exponential decay of the density of states near zero energy.~\cite{liu_soft_gap_phenomenology}
It has been shown that interface disorder, pairbreaking, tunnel barrier to normal leads, temperature, and having multimodes with different transmission probabilities, and dissipation can cause a soft induced gap~\cite{takei_soft_2013,liu_soft_gap_phenomenology,stanescu_soft_gap_2014}.
However, even without the aforementioned causes, a soft gap would still appear due to states with their momentum parallel to the junction~\cite{de_gennes_1963,beenakker_billiards_2005}.
From a semiclassical perspective, these momenta correspond to long paths through the semiconductor without interruption by the superconductor, shown in Fig.~\ref{fig:setup}(a).
These long trajectories have long flight times $\tau_\textrm{f} \approx L_\textrm{t} / v_F$ (see Fig.~\ref{fig:setup}), where $L_\textrm{t}$ is the trajectory length.
Equivalently, the Thouless energy of these trajectories $E_{\textrm{Th}}=\hbar / \tau_\textrm{f}$ is small, resulting in a small gap $E_\textrm{gap} \ll \Delta$.
This problem does not appear when the Fermi surface is small and the zero point motion dominates the transverse velocity, making a low filling of the bands a possible workaround\cite{Nijholt2015}.
However, low filling requires precise knowledge of the system and is more sensitive to disorder or microscopic inhomogeneities.
On the other hand, disorder scatters these long trajectories and introduces a cutoff on the scale of the mean free path~\cite{Haim2018}; however, disorder is impossible to control to a required precision experimentally.
